Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-18 analysis/normalized.Rmd
Minimized expressions and assignments.

nb_assigns_call_sites <- assigns %>% pull(src_ref) %>% n_distinct()
```

@@

nb_a_env_call_sites <- assign_env %>% pull(src_ref) %>% n_distinct()
```

>>>>

nb_assigns_call_sites <- assigns %>% pull(src_ref) %>% n_distinct()

r("nb assign sites", nb_assigns_call_sites)
r("assign sites percent", ratio(nb_assigns_call_sites, nb_call_sites))
```

@@

nb_a_env_call_sites <- assign_env %>% pull(src_ref) %>% n_distinct()

r("non default envir assign sites", nb_a_env_call_sites)
r("non default envir assign sites percent", ratio(nb_a_env_call_sites, nb_assigns_call_sites))
```

### 2021-03-18 paper/main.tex
Minimized expressions and assignments.

\begin{table}[h]
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Minimized & \#sites & \%sites & \#packages & \#operations & \%envir \\
		\hline
		\texttt{X} & \packageMinimizedcallsitesa  & \packageMinimizedpropsitesa & \packageMinimizedpackagea & \packageMinimizedoperationsaRnd & \packageMinimizedpercentenvira \\
		\hline
		\texttt{F(F())} & \packageMinimizedcallsitesb  & \packageMinimizedpropsitesb & \packageMinimizedpackageb  & \packageMinimizedoperationsbRnd & \packageMinimizedpercentenvirb \\
		\hline
		\texttt{V} & \packageMinimizedcallsitesc & \packageMinimizedpropsitesc & \packageMinimizedpackagec & \packageMinimizedoperationscRnd & \packageMinimizedpercentenvirc \\
		\hline
		\texttt{F(X)}& \packageMinimizedcallsitesd & \packageMinimizedpropsitesd & \packageMinimizedpackaged & \packageMinimizedoperationsdRnd & \packageMinimizedpercentenvird \\
		\hline
		\texttt{model.frame} & \packageMinimizedcallsitese & \packageMinimizedpropsitese & \packageMinimizedpackagee & \packageMinimizedoperationseRnd & \packageMinimizedpercentenvire \\
		\hline
		\texttt{\$}& \packageMinimizedcallsitesf & \packageMinimizedpropsitesf & \packageMinimizedpackagef & \packageMinimizedoperationsfRnd & \packageMinimizedpercentenvirf \\
		\hline
		\texttt{F()}& \packageMinimizedcallsitesg & \packageMinimizedpropsitesg & \packageMinimizedpackageg & \packageMinimizedoperationsgRnd & \packageMinimizedpercentenvirg \\
		\hline
		\texttt{<-} & \packageMinimizedcallsitesh & \packageMinimizedpropsitesh & \packageMinimizedpackageh & \packageMinimizedoperationshRnd & \packageMinimizedpercentenvirh \\
		\hline
		\texttt{FUN} & \packageMinimizedcallsitesi  & \packageMinimizedpropsitesi & \packageMinimizedpackagei & \packageMinimizedoperationsiRnd & \packageMinimizedpercentenviri \\
		\hline
		\texttt{\{BLOCK\}} & \packageMinimizedcallsitesj & \packageMinimizedpropsitesj & \packageMinimizedpackagej & \packageMinimizedoperationsjRnd & \packageMinimizedpercentenvirj \\
		\hline
	\end{tabular}
	\caption{Minimized expressions: ten most frequent in terms of sites. \#sites is the number of sites; \%sites the percentage of sites across the total number of sites (\packageNbCallSites sites) with at least this minimized expression; \#packages is the number of packages with at least one of the minimized expression and measures how widespread a minimized expression is. \#operations is the average number of steps performed by the R interpreter when given that minimized expression, and \%envir is the percentage of call sites for which the \c{envir} argument is explicitly passed.} \label{tab:minimizedexpressions}
\end{table}

@@

\paragraph{Composition of functions. } Compositions of functions, without variables, is the second most frequent minimized expression.

@@

@@

\paragraph{Sequence of statements.} \c{\{BLOCK\}} is a sequence of statements. It is usually large, with in average \packageMinimizedoperationsjRnd operations in it.

>>>>

\begin{table}[h]
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Minimized & \#sites & \%sites & \#packages & \#operations & \%envir \\
		\hline
		\texttt{X} & \packageMinimizedcallsitesa  & \packageMinimizedpropsitesa & \packageMinimizedpackagea & \packageMinimizedoperationsaRnd & \packageMinimizedpercentenvira \\
		\hline
		\texttt{F(F())} & \packageMinimizedcallsitesb  & \packageMinimizedpropsitesb & \packageMinimizedpackageb  & \packageMinimizedoperationsbRnd & \packageMinimizedpercentenvirb \\
		\hline
		\texttt{V} & \packageMinimizedcallsitesc & \packageMinimizedpropsitesc & \packageMinimizedpackagec & \packageMinimizedoperationscRnd & \packageMinimizedpercentenvirc \\
		\hline
		\texttt{F(X)}& \packageMinimizedcallsitesd & \packageMinimizedpropsitesd & \packageMinimizedpackaged & \packageMinimizedoperationsdRnd & \packageMinimizedpercentenvird \\
		\hline
		\texttt{model.frame} & \packageMinimizedcallsitese & \packageMinimizedpropsitese & \packageMinimizedpackagee & \packageMinimizedoperationseRnd & \packageMinimizedpercentenvire \\
		\hline
		\texttt{\$}& \packageMinimizedcallsitesf & \packageMinimizedpropsitesf & \packageMinimizedpackagef & \packageMinimizedoperationsfRnd & \packageMinimizedpercentenvirf \\
		\hline
		\texttt{F()}& \packageMinimizedcallsitesg & \packageMinimizedpropsitesg & \packageMinimizedpackageg & \packageMinimizedoperationsgRnd & \packageMinimizedpercentenvirg \\
		\hline
		\texttt{<-} & \packageMinimizedcallsitesh & \packageMinimizedpropsitesh & \packageMinimizedpackageh & \packageMinimizedoperationshRnd & \packageMinimizedpercentenvirh \\
		\hline
		\texttt{FUN} & \packageMinimizedcallsitesi  & \packageMinimizedpropsitesi & \packageMinimizedpackagei & \packageMinimizedoperationsiRnd & \packageMinimizedpercentenviri \\
		\hline
		\texttt{\{BLOCK\}} & \packageMinimizedcallsitesj & \packageMinimizedpropsitesj & \packageMinimizedpackagej & \packageMinimizedoperationsjRnd & \packageMinimizedpercentenvirj \\
		\hline
		\texttt{F(F(<-))} & \packageMinimizedcallsitesk & \packageMinimizedpropsitesk & \packageMinimizedpackagek & \packageMinimizedoperationskRnd & \packageMinimizedpercentenvirk \\
		\hline
	\end{tabular}
	\caption{Minimized expressions: ten most frequent in terms of sites. \#sites is the number of sites; \%sites the percentage of sites across the total number of sites (\packageNbCallSites sites) with at least this minimized expression; \#packages is the number of packages with at least one of the minimized expression and measures how widespread a minimized expression is. \#operations is the average number of steps performed by the R interpreter when given that minimized expression, and \%envir is the percentage of call sites for which the \c{envir} argument is explicitly passed.} \label{tab:minimizedexpressions}
\end{table}

@@

@@

\paragraph{\c{model.frame}} This is a function used to create statistical models. We explain it in more details in the section about pattern (see Section~REF).

@@

\paragraph{Assignments.} This amounts to \packageAssignSitesPercent of the sites and corresponds to minimized expressions \c{<-}, where the assignment is the top call, and \c{F(F(<-))}, where the assignment happens inside, and others that we were not enough present to be shown in table~\ref{tab:minimizedexpressions}.  Assignments are performed with \c{<-}, \c{<<-} or \c{assign}. Most often, assignment happens in top call position. A non-default environment is specified only in \packageNonDefaultEnvirAssignSitesPercent of the sites with assignments. Indeed, most of those assignments occur in the default environment, \ie in the caller of \eval. This hints that side effects are not widespread in \eval.\footnote{Side effects can also happen in a function call in the \eval expression, and that function call will hide assignment operators from us. We more precisely instrument side-effects to environment in Section~REF.}

\paragraph{Accessing a slot.}

\paragraph{Large expressions }  Compositions of functions, without variables (\c{F(F(X))} minimized expression) is the second most frequent minimized expression. \c{\{BLOCK\}} is a sequence of statements. It is usually large, with in average \packageMinimizedoperationsjRnd operations in it.
